The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-21 paper.tex
update

\begin{abstract}
A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.\
      The broad agreement between simulated and observed multiwavelength features\
      provides supporting evidence for the inclined jet scenario, and also\
      releases the caveat given by earlier simulation-based studies:\
      the jets shall be vertical to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The ambient stratification facilitates the eROSITA bubbles elongation significantly.
      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.
\item Followed by the forward shock is a tangling contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
      CRe power-law index is found to be 2.4.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they are physically related around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}

>>>>

\begin{abstract}
A decade ago, the \textit{Fermi Gamma-Ray Space Telescope} reveals two large gamma-ray bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic disk.\
The recent discovery of eROSITA bubbles also shows a symmetrically enhanced X-ray\
emission from the shells around the eROSITA bubbles.\
To this end, previous simulation-based works assumed that the jets are vertical to the Galactic disk;\
however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium disk is an essential\
component for the symmetry Galactic bubbles.\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
the oblique jets model. We find that\
(1) The Galactic bubbles are nearly symmetric about the Galactic plane albeit\
the jet is at an angle $45^{\circ}$ with respect to the disc normal.\
(2) The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
The ambient stratification facilitates the eROSITA bubbles elongation significantly.
The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc.

@@

\item The Galactic bubbles are nearly symmetric about the Galactic plane albeit the jet is at an angle $45^{\circ}$\
      with respect to the disc normal.\
      The broad agreement between simulated and observed multiwavelength features\
      provides supporting evidence for the inclined jet scenario, and also\
      releases the caveat given by earlier simulation-based studies:\
      the jets shall be vertical to the disc normal.
\item The randomness of clumpy disk has a insignificant impact on the overall dynamic of the Galactic bubbles.\
      The development of the reverse shocks (the innermost bubbles) are always associated with the dense disc,\
      without the disc, the outermost bubbles and the turbulent plasma will be oblique,\
      indicating the dense disc is crucial for\
      the symmetry of the Galactic bubbles and for the innermost bubbles formation.
\item The edge of the eROSITA bubbles is a forward shock,\
      originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
      and significantly stretched by the stratified atmosphere afterwards.\
      The simulated eROSITA bubbles are not as limb-brightened as the observed one.\
      A possibility to enhance the X-ray emission is to include shock-accelerated CRs near the shock,\
      in which CRs could increase the compressibility of the fluid.
\item Followed by the forward shock is a tangling contact discontinuity,\
      which we interpret as the edge of the \textit{Fermi} bubbles.\
      The nature of the \textit{Fermi} bubbles is essentially a turbulent and high-temperature ($\sim2$ keV)\
      plasma in pressure balance with the external medium. Associated with the Galactic magnetic field\
      will lead to the stochastic acceleration of CRe, and probably balanced with the IC and synchrotron cooling.\
      We will investigate the competition between CRe acceleration and radiative cooling in a future work.
\item According to the microwave and leptonic gamma-ray spectra, the best-fitting\
      CRe power-law index is found to be 2.4.
\item The same leptotonic CRe can simultaneously\
      account for the \textit{Fermi} bubbles and haze emission suggested that\
      they are physically related around the GC,\
      and that the magnetic fields within the bubbles are close to the exponentially distributed\
      Galactic magnetic field.
\end{itemize}
